\section{Introduction} \label{Introdcution}
Optimization problems can be found in a variety of fields and have multiple applications, for instance in the energy sector \cite{PereiraPinto1991}, logistics, machine learning and many more.
In several industrial settings, the problem is decomposed into multiple stages.
% These stages are usually determined by the  like multiple time periods
These stages are usually defined in terms of time, but are not bound to a specific number of days or hours. For example, a problem that lasts for more than a year, can still be decomposed into two stages if the problem structure only changes once.
These problems arise in a multitude of settings like fleet management \cite{example_powell_fleet_management}, supply-chain optimization \cite{example_supply_chain_optimization}, portfolio optimization \cite{example_portfolio_opt} and power scheduling in a Hydro-Thermal System \cite{example_power_scheduling_Nowak2000}.
These problems involve making decisions based on current knowledge.
After the execution of the first-stage decision, new information from the environment is observed and is used for a successive decision.
Optimization problems from this kind of problem class are called sequential decision problems \cite{Powell_solving_Curses_of_Dimensionality}.\\
% The problem class of these kind of optimization problems are called sequential decision problems \cite{Powell_solving_Curses_of_Dimensionality}.\\
Since these sequential decision problems are calculating decisions over a time frame,
it would be a strong assumption to consider them deterministic, hence they are assumed as stochastic.
One approach to solving optimization problems under uncertainty is stochastic optimization.
According to Powell \cite{POWELL2019795,Powell_Clearing_the_Jungle_of_stochastic_Optimization}, stochastic optimization has many research streams, the major ones being stochastic dynamic optimization and stochastic programming.
Stochastic programming is more common in operations research fields, while stochastic dynamic programming is used in optimal control, like in electrical engineering.
Both frameworks will be briefly discussed in this seminar paper.

This paper discusses the new advances made in the paper 'Neural Stochastic Dual Dynamic Programming' by Dai and Xue et al. \cite{NSDDP}.\\
First, a quick introduction is given to describe different frameworks in order to solve sequential optimization problems, namely stochastic programming and stochastic dynamic programming.
After that, a short overview of the major challenges of these methods is presented, namely the curse of dimensionality.
In the next section, the current state-of-the-art approaches out of the framework of stochastic programming for solving these problems are
presented, namely the L-shaped method, an extension of Benders decomposition, and stochastic dual dynamic programming.
For each approach, the pros and cons are discussed.
Moreover, the neural stochastic dual programming approach from Dai and Xue et al. \cite{NSDDP} is presented in detail with an emphasis on the advantages and disadvantages over current solving methods, and also what the limitations and constraints of this approach are.
Following that section, own computations based on my implementation of the neural stochastic dual dynamic programming approach are presented.
Finally, a conclusion and an outlook on possible future research is given.

\subsection{Stochastic Optimization}
In the following section, the frameworks of stochastic programming and stochastic dynamic optimization are discussed.
They are similar in that they both try to find an optimal policy instead of finding an optimal solution.
An optimal policy is a function that provides an optimal solution given the current known information about the environment \cite{POWELL2019795}. 
The disparities and similarities of these two approaches will be discussed in the following sections.
\input{Introduction/Stochastic_Programming}
\input{Introduction/Stochastic_Dynamic_Programming}
\input{Introduction/Curse_of_Dimensionality}